---
title: "RShinyGif"
author: "Snehanshu Tiwari"
date: "November 12, 2017"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
I am going to show something ***Amazing***.

What I am going to show you is of utmost important to this world.

So behold and watch.


```{r, echo=FALSE,message=FALSE,warning=FALSE,cache=TRUE}
library(httr)
library(rjson)
library(shiny)
str <- GET("http://api.giphy.com/v1/gifs/trending?api_key=QXjb9oXh6KmDTyxFJAhxUDXtmAoYdovg&limit=50")


json.raw <- content(str)

json.format <- rjson::fromJSON(rjson::toJSON(json.raw))

list.url <- lapply(json.format$data, function(x){x$images$original$url})

```

## Inputs and Outputs

You can embed Shiny inputs and outputs in your document. Outputs are automatically updated whenever inputs change.  This demonstrates how a standard R plot can be made interactive by wrapping it in the Shiny `renderPlot` function. The `selectInput` and `sliderInput` functions create the input widgets used to drive the plot.

```{r eruptions, echo=FALSE}
ui <- fluidPage(
  headerPanel('Internet access to everyone over past 10 years or so...'),
  sidebarPanel(
    selectInput('gif', 'Behold', list.url)
  ),
  uiOutput("image")
    )

server <- function(input, output) {
 output$image = renderUI({
    src = input$gif
    tags$img(src=src)
  })   
}


shinyApp(ui = ui, server = server)

```

## Embedded Application

It's also possible to embed an entire Shiny application within an R Markdown document using the `shinyAppDir` function. This example embeds a Shiny application located in another directory:

```{r tabsets, echo=FALSE}
shinyAppDir(
  system.file("examples/06_tabsets", package = "shiny"),
  options = list(
    width = "100%", height = 550
  )
)
```

Note the use of the `height` parameter to determine how much vertical space the embedded application should occupy.

You can also use the `shinyApp` function to define an application inline rather then in an external directory.

In all of R code chunks above the `echo = FALSE` attribute is used. This is to prevent the R code within the chunk from rendering in the document alongside the Shiny components.



